Time stability in human interaction networks, Supporting Information

### 2015-06-21 supportingInformation.tex
retoque de texto

\subsection{Time circular measures}\label{si:circ}
The measurements used were were the rescaled circular mean $\theta_\mu'$, standard deviation $S(z)$, variance $Var(z)$, circular dispersion $\delta(z)$ and the relation of maximum and minimum incidence $\frac{max(incidence)}{min(incidence)}$ at each time unit.
Also, $ \mu_{\frac{max(incidence')}{min(incidence')}} $ and $ \sigma_{\frac{max(incidence')}{min(incidence')} }$ are given for 1000 uniform distribution simulations within the same number of bins and with the same number of samples. Greater dispersion is found on seconds and minutes, followed
by days of the month. Greater localization if found in the hours of the day, followed by weekdays and months.

>>>>

\subsection{Time circular measures}\label{si:circ}
The measurements used were the rescaled circular mean $\theta_\mu'$, standard deviation $S(z)$, variance $Var(z)$, circular dispersion $\delta(z)$ and the relation of maximum and minimum incidence $\frac{max(incidence)}{min(incidence)}$ at each time unit.
Also, $ \mu_{\frac{max(incidence')}{min(incidence')}} $ and $ \sigma_{\frac{max(incidence')}{min(incidence')} }$ are given for 1000 uniform distribution simulations within the same number of bins and with the same number of samples. Greater dispersion is found on seconds and minutes, followed
by days of the month. Greater localization if found in the hours of the day, followed by weekdays and months.
